Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-08-03 Cost_manuscript.Rmd
update to recent history

```{r Setups, include = FALSE, warning = FALSE}
## libraries
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
#library(lmerTest)
library(gridExtra)
library(reshape2)
library(corrplot)
library(survival)
library(ggfortify)
library(patchwork)

@@

@@

  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) were tasked with deciding their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness. Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time). We hypothesized that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that changing the cost required to obtain rewards would uniformly increase or decrease this choice pattern. Specifically, we predicted that participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount.

>>>>

```{r Setups, include = FALSE, warning = FALSE}
## libraries
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
#library(lmerTest)
library(gridExtra)
library(reshape2)
library(corrplot)
library(survival)
library(ggfortify)
library(patchwork)
library(data.table)

@@

## UPDATE TO THIS
# IT BASICALLY SAYS THAT PEOPLE DO TRACK THE RECENT OFFERS A BIT, BEYOND WHAT H+R DO.
# AND ALSO THAT RECENT FORCED TRAVELS + QUITS DO MARGINALLY INFLUENCE CHOICE
# THIS SUGGESTS THAT WHILE THE EFFECTS ARE SMALL (P(A) ~ 2%), PARTICIPANTS DO SOME ENVIRONMENTAL TRACKING
# history
# Instead of quits, I'm now doing completions. This is because one would expect forced travels to also affect choice.
# First, iterate over the recent history to identify which sum length reduces the AIC the most
historySize <- lapply(seq(2, 6), function(tail) {
  dat <- dataBtw %>%
  group_by(SubjID) %>%
  mutate(recentTravels = seqQuits(Completed),
         recentOffers = ifelse(TrialN < (tail + 1), Offer, Reduce(`+`, shift(Offer, 1:tail)))) #%>%
  #ungroup() %>%
  glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + (1 | SubjID), data = dat, family = "binomial")
  #summarise(aic = AIC(glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + (1 | SubjID), data = ., family = "binomial")))
})

# then get the summary of the tail length that reduced the AIC the most
index <- which(sapply(historySize, function(iter) {AIC(iter)}) == min(sapply(historySize, function(iter) {AIC(iter)})))
summary(historySize[[index]])
```

@@

  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) chose their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness. Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time). We hypothesized that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that changing the cost required to obtain rewards would uniformly increase or decrease this choice pattern. Specifically, we predicted that participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount.
